Missing links and the topological robustness of food webs

### 2023-12-18 manuscript/ms_C3_v3.tex
abstract shortened

\begin{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Undersampling can lead to missing trophic interactions in recorded
  food webs, with potential consequences for the perceived functioning
  and stability of the food webs. Undersampling can be compensated for
  by using food web models such as the allometric diet breadth model
  (ADBM) to predict missing links. Simultaneously, models might predict
  links which cannot occur, i.e., real false positives.
\item
  Previous research shows that (i) food web robustness (the inverse of
  the number of secondary extinctions occurring due to primary
  extinctions) increases with connectance (the number of realised
  trophic links divided by the number of possible links), and (ii) that
  model predicted food webs usually have greater connectance than the
  observed ones. Thus, we expect that predicted food webs are more
  robust than the observed ones. However, this expectation has never, to
  our knowledge, been tested, nor has the effect size, i.e.~the
  difference in robustness of predicted and observed food web with
  respect to the difference in their connectance, been quantified.
\item
  We fill this research gap by comparing the robustness of observed food
  webs to the robustness of food webs predicted by a model (the ADBM)
  that can account for missing links. We did this for 12 different food
  webs from a wide variety of ecosystems. We used three extinction
  scenarios: random, most connected, and least connected.
\item
  We found, as expected, that the predicted food webs were more robust
  than the observed food webs, which can be attributed to the higher
  connectance of the predicted food webs. On average, for every one unit
  of increase in connectance, we found that the food webs robustness
  increased by 0.52 units for the most connected species extinction
  scenario and by 0.04 units for the random species extinction
  scenarios. On the other hand, we saw no effect or very little effect,
  on average, of increased connectance for the least connected species
  extinction scenario for all except two of the 12 food webs.
\item
  These results show that undersampling can lead to large underestimates
  of food web robustness that can be compensated for by filling in
  missing links with food web models. Also, the differences in the
  structural properties of the model predicted food webs and the
  observed food webs suggest structural properties of a food web could
  be used as summary statistics to fit models such as the ADBM to the
  observed data.
\end{enumerate}
\end{abstract}

@@

Anthropogenic changes such as climate change and habitat destruction are
a threat to biodiversity and can lead to food web collapse (Ullah et
al., 2018). This food web collapse is due to the cascades of secondary
extinctions in a food web because of the primary loss of species due to
environmental change (Pimm et al., 2006; C. D. Thomas et al., 2004; J.
A. Thomas et al., 2004). An example of a secondary extinction is when a
consumer goes extinct because its sole resource species goes extinct.
Therefore, research focused on cascading secondary extinctions, also
known as `community viability analysis', has been performed extensively
in the past few decades to quantify how robust food webs are to species
extinction (Berg et al., 2011; Dunne et al., 2002a; Dunne \& Williams,
2009; Ebenman et al., 2004; Ebenman \& Jonsson, 2005). This research
revealed that the rate of collapse of a food web depends on its
structure and complexity (Dunne et al., 2002a; Dunne \& Williams, 2009).

Simulation of primary species loss has been conducted in observed food
webs and model food webs from terrestrial and aquatic ecosystems, where
robustness was measured in terms of secondary extinctions (Dunne et al.,
2002a; Dunne \& Williams, 2009). Primary species loss is considered to
be extinction of a species due to causes external to the food web,
e.g.~overharvesting (Koning \& McIntyre, 2021), introduction of invasive
species (David et al., 2017). A secondary extinction is an extinction
caused by a previous extinction (either primary or secondary). Numerous
studies have used topological criterion for assigning a secondary
extinction to a species, i.e., if extinction is of the last resource
species of a consumer species, then the consumer species suffers
secondary extinction (Dunne et al., 2002a; Dunne \& Williams, 2009;
Sol'e \& Montoya, 2001).

@@

A key assumption of the observed food webs is that they are very well
sampled, i.e.~all the links that in reality can occur are represented.
However, it is known that not all food webs are very well sampled and do
not represent all of the feeding links that can occur (Caron et al.,
2022; Jordano, 2016; Patonai \& Jord'an, 2017). Some rare trophic links
require more sampling effort than others, whereas some trophic links
(sometimes referred to as forbidden links) remain unobserved because of
biological constraints such as spatio-temporal uncoupling, size or
reward mismatching, foraging constraints and physiological-biochemical
constraints, which are irrespective of sufficient sampling effort
(Jordano, 2016). Previous studies such as Caron et al. (2022) and Gupta
et al. (2022) have shown that the predicted food webs from these models
usually have greater connectance than the observed ones. One solution to
compensate for undersampling is using a food web model such as the
Allometric Diet Breadth Model (ADBM) (Gupta et al., 2023; Petchey et
al., 2008) to predict the missing links and then measure the robustness
of the predicted food web. The ADBM is a mechanistic model constructed
using foraging rules based on the body sizes of prey and predator, where
trophic interactions satisfying those rules would be predicted by the
model, which are perhaps not observed because those interactions are
rare. However, this solution is not infallible, as it is likely that the
food web model might still miss some links and also may predict some
links that could not, in fact occur.

In our study, we investigate the topological robustness of the ADBM
predicted food webs and compare it to that of the observed food webs. We
achieved this by simulating primary species loss in 12 food webs
predicted by the model to quantify secondary loss of extinctions and
compare the robustness of food webs predicted by the model to the
robustness of the observed food webs. We expect the model predicted food
webs to be more robust than the observed food webs, and for the greater
robustness to be related to the amount by which the model predicts
greater connectance compared to that of the observed food webs. We also
examined how different structural food web properties other than the
connectance can influence this difference in the perceived robustness.
In order to do that, we define our null hypothesis to be: (H1) The
missing links that are filled in by the model increase robustness
because they increase connectance; and our alternate hypothesis to be:
(H2) Although the model fills in missing links, it also changes other
structural properties and these outweigh the effects of connectance on
robustness.

@@

The allometric diet breadth model (ADBM) is based on optimal foraging
theory, specifically the contingency model (MacArthur \& Pianka, 1966).
We chose this model because it is known to predict greater connectance
in the predicted food webs compared to the observed food webs (Gupta et
al., 2022). The ADBM predicts the set of prey species a consumer should
feed upon to maximise its rate of energy intake (Petchey et al., 2008).
The foraging variables used in the model are the energy content of prey,
handling times of the predator on prey, space clearance rate, i.e.~how
fast a predator searches space, and prey densities. Each of these
variables is derived from the allometric scaling relationship using the
body sizes of species. More details on the foraging rules defined in the
ADBM and ADBM's predictive power across different food webs can be found
in open access Petchey et al. (2008).

@@

In the random extinction scenario, we computed robustness \(R_{50}\) for
all 1000 independent random extinction sequences and calculated the
median as a summary statistics to quantify the average robustness of a
single food web to random extinction. To quantify the effect of
undersampling, i.e.~greater connectance of connectance, we compute the
ratio of the difference in normalised robustness between the ADBM
predicted food webs and observed food webs to the difference in their
normalised connectance, where normalisation was performed by dividing
the variables by their maximum possible values (i.e.~0.5 for \(R_{50}\)
and 1 for connectance). However, we did not perform any statistical
significance test because we work with simulated food webs and
therefore, the p-values of these tests are influenced by the number of
model simulations (White et al., 2014).

@@

The model food webs were more robust than the observed food webs on
average in the most connected and random extinction scenarios (Fig.
\ref{fig:fig_r4} (a, b)). However, there were large variations in the
robustness within the model food webs in the most connected extinction
scenario (Fig. \ref{fig:fig_r4} (a)). For example, the model food webs
for the Caricaie Lakes food web was more robust than the observed food
web on average but had a larger variation in the robustness within the
model food webs compared to other food webs.

The food webs were more robust to the random extinction scenario than
the most connected scenario (Fig. \ref{fig:fig_r4} (a, b)). Small Reef
and Benguela Pelagic food webs had more variations in robustness within
the model food webs as compared to the other food webs (Fig.
\ref{fig:fig_r4} (b)). Skipwith Pond, Broadstone Stream (taxonomic
aggregation) and Broadstone Stream (size aggregation) food webs were the
most robust (Median \(R_{50} = 0.5\)) for both model and observed food
webs (Fig. \ref{fig:fig_r4} (b)). Although there were few less robust
model food webs in the Broadstone Stream (size aggregation) as shown by
the outliers.

In the least connected extinction scenario, the food webs had a very
high robustness (Median \(R_{50} = 0.5\)) for most of the food webs
(Fig. \ref{fig:fig_r4} (c)), however there were some exceptions. The
model food webs for Small Reef and Benguela Pelagic had very low median
robustness. The model food webs for the Benguela Pelagic, Broom and
Capinteria food webs had larger variations in robustness when compared
to that of the others.

@@

In all of the food webs except Broadstone Stream (taxonomic aggregation)
and Skipwith Pond, the effect size of connectance on robustness was
positive on average in the most connected extinction scenario (Fig.
\ref{fig:fig_r5} (a)), i.e.~greater connectance had a positive effect on
the robustness. In the random extinction scenario, there was a positive
effect of greater connectance on the robustness for Ythan, Small Reef,
Mill Stream, Grasslands, Caricaie Lakes, Capinteria, Broom and Benguela
Pelagic (Fig. \ref{fig:fig_r5} (b)). However, the effect size varied
across the food webs. In the least connected extinction scenario, the
median effect sizes were zero for all the food webs except for Caricaie
Lakes and Capinteria food webs where the effect sizes were very close to
zero and for Benguela Pelagic and Small Reef food webs where the median
effect sizes were negative (Fig. \ref{fig:fig_r5} (c)). However, there
were lots of outlier with effect sizes negative.

@@

As expected, the model food webs were more robust than the observed food
webs on average. The considerable variation of the robustness of the
model food webs suggests, however, that undersampling in food webs can
lead to considerable uncertainty in the estimates of food web
robustness, even when a model is used to compensate for undersampling.
Furthermore, as was previously found, the food webs are least robust to
primary extinction of the most connected species compared to that of
least connected and random extinction scenarios on average. Future
development would be to understand how undersampling, i.e.~predicted
greater connectance, influences the stability of the dynamics of the
model food webs against that of the observed food webs and compare it
with the patterns in our study in which extinction occur only by
topological criteria. However, one would expect a decrease in food web
stability with greater connectance (Martinez et al., 2006; May, 1972).

@@

As with any food web model, we expect that there are real false
positives in the food webs predicted by the ADBM. Real false positive
means that the food web model predicts a link between two species that
can never interact (The other type of false positive is when the model
predicts a link that was not observed but could have been observed if
the food web was sampled enough. In this case, further sampling should
result in the link being observed and a change from false positive to
true positive.). Firstly, this may be because the ADBM uses only body
size as a trait. A trait uncorrelated with the body size may be
influential in determining the interaction between two species (Gupta et
al., 2022). Secondly, the ADBM can only predict diets that are
contiguous with respect to the size of the prey. I.e. it cannot predict
that the consumer will consume prey of size 1 and 3, and not consume
prey of size 2. However, it is important to note that observed diets are
not always contiguous when prey are ordered by their size due to some
ecological differences in how predator species choose their prey (Caron
et al., 2022). Hence, it would be intriguing to extend our study to use
other food web models based on size-based rules, such as Gravel et al.
(2013) and Vagnon et al. (2021), to understand if the results are
dependent on the decision of model selection. We expect to get a similar
result in a size-based deterministic model but a different result,
i.e.~lower robustness in a size-based stochastic model as compared to
the ADBM because the latter can take into account non-contiguity in
predator diets (Williams et al., 2010). It would also be interesting to
use food web models not based on body size, such as Cattin et al. (2004)
and Allesina et al. (2008). We expect to have a difference in results
based on whether the trophic interactions in the food webs are governed
by size-structured rules or not.

It would be intriguing to know if this difference in connectance has a
similar influence on the dynamical stability of the food webs as well.
Hence, a prospect could be to use a dynamical model (for example, the
bioenergetic food web model by Brose et al. (2006)) to model the
temporal dynamics of the ADBM predicted food webs. We expect that the
greater connectance will lead to reduced dynamical stability in the ADBM
predicted food web compared to that of the predicted food web. The
difference in stability will be linearly related to the difference in
connectance because Martinez et al. (2006) has shown that food web
stability linearly decreases with connectance.

@@

We have used a food web model to compensate for undersampling in
recorded food webs and thereby quantified the influence of missing
links, i.e.~greater connectance on the topological robustness of 12 food
webs from various ecosystems. We found that the greater connectance can
have a large impact on the robustness of the food webs while at the same
time producing large variations in robustness among the predicted food
webs. Furthermore, differences in other structural food web properties
between the ADBM predicted food webs and the observed food webs are also
responsible.

>>>>

\begin{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Undersampling can lead to missing trophic interactions in recorded
  food webs, impacting the perceived functioning and stability of the
  food webs. Undersampling can be compensated for by using food web
  models such as the allometric diet breadth model (ADBM) to predict
  missing links. Simultaneously, models might predict links which cannot
  occur, i.e., real false positives.
\item
  Previous research shows that (i) food web robustness increases with
  connectance, and (ii) that model predicted food webs usually have
  greater connectance than the observed ones. Thus, we expect that
  predicted food webs with fewer missing links are more robust than the
  observed ones. However, this expectation has never, to our knowledge,
  been tested, nor has the effect size, i.e.~the difference in
  robustness of predicted and observed food web with respect to the
  difference in their connectance, been quantified.
\item
  We fill this research gap by comparing the robustness of observed food
  webs to the robustness of food webs predicted by a model (the ADBM)
  that can account for missing links. We did this for 12 different food
  webs from a wide variety of ecosystems. We used three extinction
  scenarios: random, most connected first, and least connected first.
\item
  We found, as expected, that predicted food webs were more robust than
  observed food webs, which can be attributed to the higher connectance
  of the predicted food webs. On average, a one-unit rise in connectance
  corresponded to a 0.52-unit increase in robustness for the most
  connected species extinction scenario and a 0.04-unit increase for
  random species extinction scenarios. Interestingly, the least
  connected species extinction scenario showed minimal or no effect on
  increased connectance, on average, for most food webs, except for two.
\item
  These results emphasize the significant underestimation of food web
  robustness caused by undersampling, mitigated by filling in missing
  links using models. Moreover, differences in the structural properties
  of the model predicted food webs, such as proportion of basal species
  and maximum trophic height can have large effects on robustness and
  therefore could be used to further constrain predicted food webs and
  perhaps produce more constrained predictions of food web robustness.
\end{enumerate}
\end{abstract}

@@

Anthropogenic changes such as climate change and habitat destruction are
a threat to biodiversity and can lead to food web collapse (Ullah et
al., 2018). This food web collapse is due to the cascades of secondary
extinctions in a food web because of the primary loss of species due to
environmental change and anthropogenic impacts (Pimm et al., 2006; C. D.
Thomas et al., 2004; J. A. Thomas et al., 2004). An example of a
secondary extinction is when a consumer goes extinct because its sole
resource species goes extinct. Therefore, research about cascades of
secondary extinctions, also known as `community viability analysis', has
been performed extensively in the past few decades to quantify how
robust food webs are to species extinction (Berg et al., 2011; Dunne et
al., 2002a; Dunne \& Williams, 2009; Ebenman et al., 2004; Ebenman \&
Jonsson, 2005). This research revealed that the rate of collapse of a
food web depends on its structure and complexity (Dunne et al., 2002a;
Dunne \& Williams, 2009).

Simulation of the effects of primary species loss has been conducted in
observed food webs and in model food webs from terrestrial and aquatic
ecosystems, where robustness was measured in terms of secondary
extinctions (Dunne et al., 2002a; Dunne \& Williams, 2009). Primary
species loss is considered to be extinction of a species due to causes
external to the food web, e.g.~overharvesting (Koning \& McIntyre,
2021), introduction of invasive species (David et al., 2017). A
secondary extinction is an extinction caused by a previous extinction
(either primary or secondary). Numerous studies have used topological
criterion for assigning a secondary extinction to a species, i.e., if
extinction is of the last resource species of a consumer species, then
the consumer species suffers secondary extinction (Dunne et al., 2002a;
Dunne \& Williams, 2009; Sol'e \& Montoya, 2001).

@@

A key assumption of the observed food webs is that they are very well
sampled, i.e.~all the links that in reality can occur are represented.
However, it is known that not all food webs are very well sampled and do
not represent all of the feeding links that can occur (Caron et al.,
2022; Jordano, 2016; Patonai \& Jord'an, 2017). Some rare trophic links
require more sampling effort than others, whereas some trophic links
(sometimes referred to as forbidden links) remain unobserved because of
biological constraints such as spatio-temporal uncoupling, size or
reward mismatching, foraging constraints and physiological-biochemical
constraints, which are irrespective of sufficient sampling effort
(Jordano, 2016). Previous studies such as Caron et al. (2022) and Gupta
et al. (2022) have shown that the predicted food webs from these models
usually have greater connectance than the observed ones. One solution to
compensate for undersampling is, therefore, to use a food web model such
as the Allometric Diet Breadth Model (ADBM) (Gupta et al., 2023; Petchey
et al., 2008) to predict the missing links and then measure the
robustness of the predicted food web. The ADBM is a mechanistic model
constructed using foraging rules based on the body sizes of prey and
predator, where trophic interactions satisfying those rules would be
predicted by the model, which are perhaps not observed because those
interactions are rare. However, this solution is not infallible, as it
is likely that the food web model might still miss some links and also
may predict some links that could not, in fact occur.

In our study, we investigate the topological robustness of the ADBM
predicted food webs and compare it to that of the observed food webs. We
achieved this by simulating primary species loss in 12 food webs
predicted by the model to quantify secondary loss of extinctions and
comparing the robustness of food webs predicted by the model to the
robustness of the observed food webs. We expect the model predicted food
webs to be more robust than the observed food webs, and for the greater
robustness to be related to the amount by which the model predicts
greater connectance compared to that of the observed food webs. We also
examined how structural food web properties other than the connectance
can influence this difference in the perceived robustness. In order to
do that, we define our null hypothesis to be: (H1) The missing links
that are filled in by the model increase robustness because they
increase connectance; and our alternate hypothesis to be: (H2) Although
the model fills in missing links, it also changes other structural
properties and these outweigh the effects of connectance on robustness.

@@

The allometric diet breadth model (ADBM) is based on optimal foraging
theory, specifically the contingency model (MacArthur \& Pianka, 1966).
We chose this model because it is known to predict greater connectance
in the predicted food webs compared to the observed food webs (Gupta et
al., 2022). The ADBM predicts the set of prey species a consumer should
feed upon to maximise its rate of energy intake (Petchey et al., 2008).
The foraging variables used in the model are the energy content of prey,
handling times of the predator on prey, space clearance rate, i.e.~how
fast a predator searches space, and prey densities. Each of these
variables is derived from the allometric scaling relationship using the
body sizes of species. More details on the foraging rules defined in the
ADBM and it's predictive power across different food webs can be found
in open access Petchey et al. (2008).

@@

In the random extinction scenario, we computed robustness \(R_{50}\) for
all 1000 independent random extinction sequences and calculated the
median as a summary statistics to quantify the average robustness of a
single food web to random extinction. To quantify the effect of
undersampling, we computed the ratio of the difference in normalised
robustness between the ADBM predicted food webs and observed food webs
to the difference in their normalised connectance. Normalisation was
performed by dividing the variables by their maximum possible values
(i.e.~0.5 for \(R_{50}\) and 1 for connectance). However, we did not
perform any statistical significance test because we work with simulated
food webs and therefore, the p-values of these tests are influenced by
the number of model simulations (White et al., 2014).

@@

The model food webs were more robust than the observed food webs on
average in the most connected and random extinction scenarios (Fig.
\ref{fig:fig_r4} (a, b)). However, there were large variations in the
robustness within the model food webs in the most connected extinction
scenario (Fig. \ref{fig:fig_r4} (a)). For example, the model food webs
for the Caricaie Lakes food web were more robust than the observed food
web on average but had a larger variation in the robustness within the
model food webs compared to other food webs.

The food webs were more robust to the random extinction scenario than
the most connected scenario (Fig. \ref{fig:fig_r4} (a, b)). Small Reef
and Benguela Pelagic food webs had more variations in robustness within
the model food webs as compared to the other food webs (Fig.
\ref{fig:fig_r4} (b)). Skipwith Pond, Broadstone Stream (taxonomic
aggregation) and Broadstone Stream (size aggregation) food webs were the
most robust (Median \(R_{50} = 0.5\)) for both model and observed food
webs (Fig. \ref{fig:fig_r4} (b)).

In the least connected extinction scenario, the food webs had a very
high robustness (Median \(R_{50} = 0.5\)) for most of the food webs
(Fig. \ref{fig:fig_r4} (c)). However there were some exceptions. The
model food webs for Small Reef and Benguela Pelagic had very low median
robustness. The model food webs for the Benguela Pelagic, Broom and
Capinteria food webs had larger variations in robustness when compared
to that of the others.

@@

In all of the food webs except Broadstone Stream (taxonomic aggregation)
and Skipwith Pond, the effect size of connectance on robustness was
positive on average in the most connected extinction scenario (Fig.
\ref{fig:fig_r5} (a)), i.e.~greater connectance had a positive effect on
the robustness. In the random extinction scenario, there was a positive
effect of greater connectance on the robustness for Ythan, Small Reef,
Mill Stream, Grasslands, Caricaie Lakes, Capinteria, Broom and Benguela
Pelagic (Fig. \ref{fig:fig_r5} (b)). However, the effect size varied
across the food webs. In the least connected extinction scenario, the
median effect sizes were zero for all the food webs except for Caricaie
Lakes and Capinteria food webs where the effect sizes were very close to
zero and for Benguela Pelagic and Small Reef food webs where the median
effect sizes were negative (Fig. \ref{fig:fig_r5} (c)). However, there
were many outliers with effect sizes negative.

@@

As expected, the model food webs were more robust than the observed food
webs on average. The considerable variation of the robustness of the
model food webs suggests, however, that undersampling in food webs can
lead to considerable uncertainty in the estimates of food web
robustness, even when a model is used to compensate for undersampling.
Furthermore, as was previously found, the food webs are least robust to
primary extinction of the most connected species compared to that of
least connected and random extinction scenarios on average. Future
development would be to understand how undersampling, i.e.~predicted
greater connectance, influences the stability of the dynamics of the
model food webs against that of the observed food webs and compare it
with the patterns in our study in which extinction occur only by
topological criteria. One would at least expect a decrease in food web
stability with greater connectance (Martinez et al., 2006; May, 1972).

@@

As with any food web model, we expect that there are real false
positives in the food webs predicted by the ADBM. Real false positive
means that the food web model predicts a link between two species that
can never interact. (The other type of false positive is when the model
predicts a link that was not observed but could have been observed if
the food web was sampled enough. In this case, further sampling should
result in the link being observed and a change from false positive to
true positive.). Firstly, this may be because the ADBM uses only body
size as a trait. A trait uncorrelated with the body size may be
influential in determining the interaction between two species (Gupta et
al., 2022). Secondly, the ADBM can only predict diets that are
contiguous with respect to the size of the prey. I.e., it cannot predict
that the consumer will consume prey of size 1 and 3, and not consume
prey of size 2. However, it is important to note that observed diets are
not always contiguous when prey are ordered by their size due to some
ecological differences in how predator species choose their prey (Caron
et al., 2022). Hence, it would be intriguing to extend our study to use
other food web models based on size-based rules, such as Gravel et al.
(2013) and Vagnon et al. (2021), to understand if the results are
dependent on the decision of model selection. We expect to get a similar
result in a size-based deterministic model but a different result, i.e.,
lower robustness in a size-based stochastic model as compared to the
ADBM because the latter can take into account non-contiguity in predator
diets (Williams et al., 2010). It would also be interesting to use food
web models not based on body size, such as Cattin et al. (2004) and
Allesina et al. (2008). We expect to have a difference in results based
on whether the trophic interactions in the food webs are governed by
size-structured rules or not.

It would be intriguing to know if the difference in connectance has a
similar influence on the dynamical stability of the food webs as well.
Hence, a prospect could be to use a dynamical model (for example, the
bioenergetic food web model by Brose et al. (2006)) to model the
temporal dynamics of the ADBM predicted food webs. We expect that the
greater connectance will lead to reduced dynamical stability in the ADBM
predicted food web compared to that of the predicted food web. The
difference in stability will be linearly related to the difference in
connectance because Martinez et al. (2006) has shown that food web
stability linearly decreases with connectance.

@@

We have used a food web model to compensate for undersampling in
recorded food webs and thereby quantified the influence of missing
links, i.e., greater connectance on the topological robustness of 12
food webs from various ecosystems. We found that the greater connectance
can have a large impact on the robustness of the food webs while at the
same time producing large variations in robustness among the predicted
food webs. Furthermore, differences in other structural food web
properties between the ADBM predicted food webs and the observed food
webs are also responsible.
